TEMPERATURES AND METALLICITIES FOR 10,000 M DWARFS\\ IN THE \apogee\ SURVEY

### 2019-01-23 paper/draft.tex
improved figures
add line list table

\newcommand{\apogee}{\textsl{APOGEE}}
\newcommand{\thecannon}{\textsl{The Cannon}}
\newcommand{\cannon}{\textsl{Cannon}}
\newcommand{\aspcap}{\textsl{ASPCAP}}
\newcommand{\gaia}{\textsl{Gaia}}
\newcommand{\zmass}{\textsl{2MASS}}
\newcommand{\sdss}{\textsl{SDSS}}
\newcommand{\lamost}{\textsl{LAMOST}}
\newcommand{\sdssiv}{\textsl{SDSS-IV}}
\newcommand{\tess}{\textsl{TESS}}
\newcommand{\teff}{$T_{\rm eff}$}

@@

\begin{figure}[ht]
\plotone{figures/self_and_validation_test_teff_snr.png}
\plotone{figures/self_and_validation_test_feh_snr.png}
\caption{Consistency test for the Mann-trained temperature/metallicity type model; self-test (left), and leave-one-out cross validation (right). Sources with strong rotational broadening (2M07171706--0501031, 2M08155393+3136392, 2M09174473+4612246, 2M10331367+3409120, 2M15594729+4403595, 2M13400879+4346380), as identified by visual inspection are marked with red circles. Predictive accuracy, as computed by the scatter in cross validation is 77K in temperature, and 0.09 dex in metallicity.}\label{fig:mann_validation}
\end{figure}

@@

\begin{figure}[ht]
% \gridline{\fig{figures/safe_selection_teff.png}{0.5\textwidth}{}
%           \fig{figures/safe_selection_feh.png}{0.5\textwidth}{}}
% \gridline{\fig{figures/safe_selection_spt.png}{0.5\textwidth}{}}
\plottwo{figures/cmd_teff_full.png}{figures/cmd_teff_safe.png}
\plottwo{figures/cmd_feh_full.png}{figures/cmd_feh_safe.png}
\plottwo{figures/cmd_spt_full.png}{figures/cmd_spt_safe.png}
\caption{Full sample of 14,827 M dwarfs colored by \cannon\ labels before selection (left) and final sample selection of 10,311 M dwarfs after applying selection criteria described in Section \ref{subsec:test_selection} (right), to reduce contamination from sources with that are not similar to the training sample (not single, main-sequence M stars, such as pre-main sequence, binaries, and K dwarfs). Overplotted with orange triangles are the M15 and W11 training samples, for their respective \cannon\ test labels. Temperature gradient increases with decreasing color, spectral subtype increases with increasing color, and metallicity gradient increases perpendicularly up from the main sequence branch as expected. Deviations from these gradients seen at the upper slice of the main sequence is likely remaining contamination from the binary sequence. \label{fig:safe_selection}}
\end{figure}

@@

>>>>

\newcommand{\apogee}{\textsl{APOGEE}}
\newcommand{\thecannon}{\textsl{The Cannon}}
\newcommand{\cannon}{\textsl{Cannon}}
\newcommand{\aspcap}{\textsl{ASPCAP}}
\newcommand{\gaia}{\textsl{Gaia}}
\newcommand{\zmass}{\textsl{2MASS}}
\newcommand{\sdss}{\textsl{SDSS}}
\newcommand{\lamost}{\textsl{LAMOST}}
\newcommand{\sdssiv}{\textsl{SDSS-IV}}
\newcommand{\tess}{\textsl{TESS}}
\newcommand{\teff}{$T_{\rm eff}$}
\newcommand{\feh}{[Fe/H]}

@@

\begin{figure}[ht]
% \plotone{figures/self_and_validation_test_teff_snr.png}
% \plotone{figures/self_and_validation_test_feh_snr.png}
\plottwo{figures/crv_test_teff.png}{figures/crv_test_fe_h.png}
\caption{Consistency test for the Mann-trained temperature/metallicity type model; self-test (left), and leave-one-out cross validation (right). Sources with strong rotational broadening (2M07171706--0501031, 2M08155393+3136392, 2M09174473+4612246, 2M10331367+3409120, 2M15594729+4403595, 2M13400879+4346380), as identified by visual inspection are marked with red circles. Predictive accuracy, as computed by the scatter in cross validation is 77K in temperature, and 0.09 dex in metallicity.}\label{fig:mann_validation}
\end{figure}

@@

\begin{figure}[ht]
\plottwo{figures/cmd_teff_full.png}{figures/cmd_teff_safe.png}
\plottwo{figures/cmd_feh_full.png}{figures/cmd_feh_safe.png}
\plottwo{figures/cmd_spt_full.png}{figures/cmd_spt_safe.png}
\caption{Full sample of 14,827 M dwarfs colored by \cannon\ labels before selection (left) and final sample selection of 10,311 M dwarfs after applying selection criteria described in Section \ref{subsec:test_selection} (right), to reduce contamination from sources with that are not similar to the training sample (not single, main-sequence M stars, such as pre-main sequence, binaries, and K dwarfs). Overplotted with orange triangles are the M15 and W11 training samples, for their respective \cannon\ test labels. Temperature gradient increases with decreasing color, spectral subtype increases with increasing color, and metallicity gradient increases perpendicularly up from the main sequence branch as expected. Deviations from these gradients seen at the upper slice of the main sequence is likely remaining contamination from the binary sequence. \label{fig:safe_selection}}
\end{figure}

@@

\begin{deluxetable*}{|c|c|c|c|c|}
\tablecaption{Strong \teff\ correlated lines for all features with significance greater than $2\sigma_{\rm jackknife}$.}
\tablehead{Species & Wavelength & Derivative & $\sigma_{\rm jackknife}$ & Significance}
\startdata
Fe I & 15207.509 & -0.007 & 0.003 & -2.622 \\
Fe I & 15648.478 & -0.006 & 0.002 & -3.273 \\
Fe I & 15692.643 & -0.008 & 0.002 & -4.056 \\
FeH & 16107.127 & -0.002 & 0.001 & -2.78 \\
FeH & 16245.463 & -0.005 & 0.002 & -3.214 \\
FeH & 16271.519 & -0.002 & 0.001 & -2.013 \\
FeH & 16284.562 & -0.006 & 0.001 & -5.807 \\
FeH & 16377.066 & -0.005 & 0.001 & -4.554 \\
FeH & 16741.489 & -0.002 & 0.001 & -2.873 \\
FeH & 16812.415 & -0.004 & 0.001 & -4.241 \\
FeH & 16813.808 & -0.006 & 0.001 & -3.954 \\
FeH & 16922.405 & -0.003 & 0.001 & -3.867 \\
FeH & 16934.801 & -0.004 & 0.001 & -3.591 \\
OH & 15278.267 & 0.006 & 0.003 & 2.47 \\
OH & 15280.8 & 0.004 & 0.002 & 2.007 \\
OH & 15391.186 & 0.006 & 0.003 & 2.127 \\
OH & 15407.355 & 0.01 & 0.002 & 4.836 \\
OH & 15409.271 & 0.008 & 0.002 & 4.683 \\
OH & 15505.797 & 0.009 & 0.003 & 3.511 \\
OH & 15560.305 & 0.008 & 0.002 & 3.865 \\
OH & 15565.895 & 0.005 & 0.002 & 2.505 \\
OH & 15568.691 & 0.007 & 0.001 & 4.929 \\
OH & 15572.133 & 0.008 & 0.002 & 4.393 \\
OH & 16052.7 & 0.008 & 0.002 & 3.517 \\
OH & 16055.362 & 0.006 & 0.002 & 3.7 \\
OH & 16061.796 & 0.007 & 0.003 & 2.502 \\
OH & 16065.124 & 0.009 & 0.002 & 4.214 \\
OH & 16069.564 & 0.008 & 0.003 & 3.275 \\
OH & 16074.227 & 0.007 & 0.002 & 3.338 \\
OH & 16190.345 & 0.007 & 0.003 & 2.498 \\
OH & 16192.134 & 0.008 & 0.002 & 4.012 \\
OH & 16203.995 & 0.006 & 0.002 & 3.039 \\
OH & 16207.129 & 0.004 & 0.002 & 2.196 \\
OH & 16352.196 & 0.007 & 0.002 & 3.609 \\
OH & 16354.682 & 0.011 & 0.003 & 4.167 \\
OH & 16364.626 & 0.007 & 0.003 & 2.661 \\
OH & 16368.244 & 0.008 & 0.002 & 4.303 \\
OH & 16581.281 & 0.008 & 0.002 & 4.41 \\
OH & 16581.74 & 0.004 & 0.001 & 4.842 \\
OH & 16866.621 & 0.005 & 0.001 & 3.169 \\
OH & 16871.982 & 0.012 & 0.002 & 4.892 \\
OH & 16878.976 & 0.006 & 0.002 & 3.807 \\
OH & 16884.573 & 0.005 & 0.002 & 3.066 \\
OH & 16886.206 & 0.006 & 0.001 & 5.131 \\
OH & 16895.074 & 0.005 & 0.002 & 2.197 \\
Si I & 15960.044 & -0.009 & 0.004 & -2.523 \\
Si I & 16094.893 & -0.014 & 0.003 & -4.368 \\
Si I & 16680.77 & -0.01 & 0.003 & -3.475 \\
K I & 15162.824 & -0.006 & 0.002 & -2.294 \\
Ti I & 15715.641 & 0.006 & 0.002 & 2.894 \\
Ti I & 16634.973 & 0.003 & 0.001 & 4.224 \\
V I & 15923.924 & 0.003 & 0.001 & 3.6 \\
Mn I & 15159.054 & -0.006 & 0.002 & -3.123 \\
\enddata
\end{deluxetable*}

\begin{deluxetable*}{|c|c|c|c|c|}
\tablecaption{Strong \feh\ correlated lines for all features with significance greater than $2\sigma_{\rm jackknife}$.}
\tablehead{Species & Wavelength & Derivative & $\sigma_{\rm jackknife}$ & Significance}
\startdata
Fe I & 15490.381 & -0.004 & 0.001 & -2.722 \\
Fe I & 15692.643 & -0.005 & 0.002 & -2.759 \\
Fe I & 16009.512 & -0.006 & 0.003 & -2.143 \\
FeH & 16114.027 & 0.004 & 0.001 & 2.673 \\
FeH & 16574.64 & 0.003 & 0.001 & 2.356 \\
FeH & 16694.372 & 0.003 & 0.001 & 2.193 \\
FeH & 16814.041 & 0.004 & 0.002 & 2.513 \\
OH & 16052.7 & 0.005 & 0.002 & 2.034 \\
OH & 16055.362 & 0.006 & 0.002 & 2.805 \\
OH & 16065.124 & 0.007 & 0.003 & 2.364 \\
OH & 16871.982 & 0.007 & 0.003 & 2.306 \\
OH & 16886.206 & 0.004 & 0.001 & 2.52 \\
Si I & 15960.044 & -0.007 & 0.003 & -2.112 \\
Si I & 16680.77 & -0.006 & 0.003 & -2.156 \\
K I & 15163.033 & 0.006 & 0.003 & 2.043 \\
V I & 15923.924 & 0.002 & 0.001 & 2.017 \\
Cr I & 15680.073 & -0.005 & 0.002 & -2.811 \\
Mn I & 15159.054 & -0.008 & 0.002 & -3.298 \\
Mn I & 15262.023 & -0.005 & 0.002 & -2.996 \\
\enddata
\end{deluxetable*}
